\boldmath Supersymmetric Dirac-Born-Infeld Axionic Inflation and Non-Gaussianity

### 2018-11-04 SUSY_DBI_referee_reply.tex

 \begin{center}
 Reply to report of referee
  \end{center}

{\it We thank the referee for his/her comments and suggestions.
In the revised version we have taken account of these comments and suggestions.
Below are our brief replies to the referee report.}

\noindent
Referee:\\
 The paper studies inflation and non-Gaussianity in a two-field supersymmetric DBI model. The paper is of some interest, but I have several questions and a few suggestions for improvement before I can formulate a recommendation.\\

1) What value of m in (3.11) is taken in the concrete numerical evaluations?\\
 \noindent {\it Reply\\
 In the analysis we have taken $m=6$. We also added a corresponding note to the paper in
 the captions of Fig.(1) and Fig.(3) in Sec.(6).

@@

2) Nearly all relations in the paper are given in an implicit way, (for example keeping derivatives of the superpotential unspecified). In my opinion, the paper would improve if it showed the following explicit results:\\

 {\it Reply\\
 The derivatives of the superpotential first appear in Eq. (3.12) because their explicit forms were not needed in the
 immediate discussion that follows Eq. (3.12). They were made explicit in Eqs.(3.20), (3.21), (3.23)-(3.26). 
 However, we are happy to make them explicit immediately after Eq. (3.12) which we have done in the two unnumbered equations 
 after Eq.(3.12) in the revised version of the paper.
 Similarly we have added a line after \bl{Eq.(3.7)} directing the reader to section 8 (an appendix) where the covariant derivatives
 are defined.
 }

### 2018-12-02 SUSY_DBI.tex
Small typo fixes and clarifications (#15)
In going over the new version of the paper in GiHub, I noticed one minor typo which I corrected. Also in the reply I have made a small addition to item 1).
Modify the paper to have T << 1 (#17)
# Changes

* Closes https://github.com/maxitg/susy-dbi/issues/16.
* Modifies Figures and text to use the value of $T = 10^{-12}$ (no major changes).
* Adds Fig.5, showing histograms of Hubble parameter at horizon exit, and of the mass of $a_-$.

  linear combination of axion fields is corresponds to the pseudo-Nambu-Goldstone bosons (pNGB)  and is massless. On including $W_{sb}$ in

@@

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig1.pdf}
    \caption{Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the
      scalar spectral index $n_s$ for the two field DBI model.
      The blue region enclosed by the blue line is the one allowed by experiment in the 2$\sigma$
      range. $89\%$ of the simulated points are consistent with Planck constraints as shown by green
      points while the red points lie outside the 68\% CL contour.
          Right panel: A plot of non-Gaussianity parameter $f^{equil}_{NL}$ as
      a function of $\alpha_1$ for the same data set as in the left plot. As in the left panel
      the green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region and the red dots are parameter points which are
      outside the experimentally allowed region on $r$ and $n_s$.
          There are $0.5 \times 10^6$ points shown which are distributed according to the following:
      $\alpha_1 \sim X_{0, \infty}$, $\alpha_2 = \alpha_3 = 0$,
      $T = M_\text{P}^4$,
      $f \sim X_{0, \infty} M_\text{P}$,
      $\tilde\beta \sim X_{0, \infty}$,
      $m = 6$, % G_7 = G_8 = ... = 0
      ${\cal{G}}_1 = {\cal{G}}_2 = {\cal{G}}_3 = 0$, ${\cal{G}}_4 = 1$,
      ${\cal{G}}_5 \sim {\cal{G}}_6 \sim \mathcal{U}\left\{-1, 1\right\} \times X_{0, \infty}$,
      $N_{\rm pivot} \sim \mathcal{U}\left(50, 60\right)$,
      $a_{-, 0} \sim \mathcal{U}\left(0, 2\pi\right) \times f$,
      $\dot a_{-, 0} \sim \mathcal{U}\left(-1, 1\right)
          \times \left(2 \sqrt{T}/\left(\sqrt{2} \sqrt{\alpha_1} + 2\right)^{1/2}\right)$
      where $X_{0, \infty} = \mathcal{U}\left\{X_{0, 1}, 1 / X_{0, 1}\right\}$,
      $X_{0, 1} = \mathcal{U}\left(0, 1\right)$, $\mathcal{U}$ refers to a uniform distribution,
      and the distribution of $\dot a_{-, 0}$ is chosen such that the expression under the
      square root in Eq.~(\ref{eq.axionLagrangian.I}) is positive.}
    \label{fig1}
  \end{figure}

@@

  \begin{figure}
  	\centering
  	\includegraphics[width=1.0\textwidth]{figs/fig3.pdf}
  	\caption{The effect of $\alpha_2$ (left panel) and $\alpha_3$ (right panel) on non-Gaussianity for a parameter point 
	taken from Fig.~(\ref{fig1}) which is consistent with 
	Planck data and has the  largest non-Gaussianity among the set of parameter points 
  in Fig.~(\ref{fig1}). Specifically, here $f = 0.429 M_\text{P}$, $a_{-, 0} = 0.233 M_\text{P}$, $\dot a_{-, 0} = -0.118 M_\text{P}^2$, $m = 6$, ${\cal{G}}_1 = {\cal{G}}_2 = {\cal{G}}_3 = 0$, ${\cal{G}}_4 = 1$, ${\cal{G}}_5 = -1.53$, ${\cal{G}}_6 = 563$, $\alpha_1 = 1207$, $\tilde \beta = 0.802$, $T = M_\text{P}^4$. One
	finds that
	 the effect is not sufficient to obtain a significantly larger value of $f_\text{NL}$.}
  	\label{fig3}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig4.pdf}
    \caption{
      Left panel: A plot of $f / M_{\rm P}$ as a function of $n_s$ which is in the allowed range of
      experiment and $N_{\rm pivot}$ in the range $50-60$ for the same data set as in
      Fig.~(\ref{fig1}).
      Right panel: The same as the left panel except that the plot is of $f / M_{\rm P}$ as a
      function of $r$.
      We note that the plots show that there are a large number of parameter points where
      $f / M_{\rm P} < 1$ consistent with all the experimental data.}
    \label{fig4}
  \end{figure}

@@

  Finally in Fig.(\ref{fig4}) we exhibit that the analysis contains a significant part of the parameter space where
  inflation consistent with the desired number of e-foldings in the range $[50,60]$ and $n_s$ and $r$ consistent
  with Planck data can be gotten in the axion inflation model with $f/M_{\rm P} <1$. Thus the left panel
  of Fig. (\ref{fig4}) exhibits $f/M_{\rm P}$ as a function of $n_s$ in the range allowed by the Planck data constraint of Eq.(\ref{data})
  and the right panel of Fig. (\ref{fig4}) gives $f/M_{\rm P}$ as a function of $r$
  containing the range in $r$ consistent with the Planck data constraint of Eq.(\ref{data}).

>>>>

  linear combination of axion fields corresponds to the pseudo-Nambu-Goldstone bosons (pNGB)  and is massless. On including $W_{sb}$ in

@@

  Note that there are two ways here to achieve $A_k \ll \mu \approx M_\text{P}$, which is the
  condition needed for slow-roll approximation.
  One way is to consider small values of $\tilde\beta$, in which case we found DBI plays
  insignificant role and we reproduce the results of~\cite{Nath:2017ihp}.
  Another way is to consider $T \ll M_\text{P}$, and $\tilde\beta \approx M_\text{P}$, which is the
  case we will focus on for the remainder of this paper.

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig1.pdf}
    \caption{Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the
      scalar spectral index $n_s$ for the two field DBI model.
      The blue region enclosed by the blue line is the one allowed by experiment in the 2$\sigma$
      range. $89\%$ of the simulated points are consistent with Planck constraints as shown by green
      points while the red points lie outside the 68\% CL contour.
          Right panel: A plot of non-Gaussianity parameter $f^{equil}_{NL}$ as
      a function of $\alpha_1$ for the same data set as in the left plot. As in the left panel
      the green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region and the red dots are parameter points which are
      outside the experimentally allowed region on $r$ and $n_s$.
          Points are distributed according to the following:
      $\alpha_1 \sim X_{0, \infty}$, $\alpha_2 = \alpha_3 = 0$,
      $T = 10^{-12} M_\text{P}^4$,
      $f \sim X_{0, \infty} M_\text{P}$,
      $\tilde\beta \sim X_{0, \infty}$,
      $m = 6$, % G_7 = G_8 = ... = 0
      ${\cal{G}}_1 = {\cal{G}}_2 = {\cal{G}}_3 = 0$, ${\cal{G}}_4 = 1$,
      ${\cal{G}}_5 \sim {\cal{G}}_6 \sim \mathcal{U}\left\{-1, 1\right\} \times X_{0, \infty}$,
      $N_{\rm pivot} \sim \mathcal{U}\left(50, 60\right)$,
      $a_{-, 0} \sim \mathcal{U}\left(0, 2\pi\right) \times f$,
      $\dot a_{-, 0} \sim \mathcal{U}\left(-1, 1\right)
          \times \left(2 \sqrt{T}/\left(\sqrt{2} \sqrt{\alpha_1} + 2\right)^{1/2}\right)$
      where $X_{0, \infty} = \mathcal{U}\left\{X_{0, 1}, 1 / X_{0, 1}\right\}$,
      $X_{0, 1} = \mathcal{U}\left(0, 1\right)$, $\mathcal{U}$ refers to a uniform distribution,
      and the distribution of $\dot a_{-, 0}$ is chosen such that the expression under the
      square root in Eq.~(\ref{eq.axionLagrangian.I}) is positive.
      Points are further filtered such that the mass of the inflaton $m_{a_-} < 0.1 M_\text{P}$.}
    \label{fig1}
  \end{figure}

@@

  \begin{figure}
  	\centering
  	\includegraphics[width=1.0\textwidth]{figs/fig3.pdf}
  	\caption{The effect of $\alpha_2$ (left panel) and $\alpha_3$ (right panel) on non-Gaussianity for a parameter point 
	taken from Fig.~(\ref{fig1}) which is consistent with 
	Planck data and has the  largest non-Gaussianity among the set of parameter points 
  in Fig.~(\ref{fig1}). Specifically, here $f = 0.429 M_\text{P}$, $a_{-, 0} = 0.233 M_\text{P}$, $\dot a_{-, 0} = -0.118 M_\text{P}^2$, $m = 6$, ${\cal{G}}_1 = {\cal{G}}_2 = {\cal{G}}_3 = 0$, ${\cal{G}}_4 = 1$, ${\cal{G}}_5 = -1.53$, ${\cal{G}}_6 = 563$, $\alpha_1 = 1207$, $\tilde \beta = 0.802$, $T = 10^{-12} M_\text{P}^4$. One
	finds that
	 the effect is not sufficient to obtain a significantly larger value of $f_\text{NL}$.}
  	\label{fig3}
  \end{figure}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig4.pdf}
    \caption{
      Left panel: A plot of $f / M_{\rm P}$ as a function of $n_s$ which is in the allowed range of
      experiment and $N_{\rm pivot}$ in the range $50-60$ for the same data set as in
      Fig.~(\ref{fig1}).
      Right panel: The same as the left panel except that the plot is of $f / M_{\rm P}$ as a
      function of $r$.
      We note that the plots show that there are a large number of parameter points where
      $f / M_{\rm P} < 1$ consistent with all the experimental data. Also note there are
      experimentally consistent points with $f/M_{\rm P} \in \left[0.1, 1\right]$.}
    \label{fig4}
  \end{figure}

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig5.pdf}
    \caption{
      Left panel: A histogram of the values of Hubble parameter at horizon exit for the same
      data set in Fig.~(\ref{fig1}) for points that are consistent (green) and not consistent (red)
      with experimental constraints on $r$ and $n_s$.
      Right panel: The same as the left panel except the histogram of the inflaton $a_-$ mass is
      shown instead.}
    \label{fig5}
  \end{figure}

@@

  Then, in Fig.(\ref{fig4}) we exhibit that the analysis contains a significant part of the parameter space where
  inflation consistent with the desired number of e-foldings in the range $[50,60]$ and $n_s$ and $r$ consistent
  with Planck data can be gotten in the axion inflation model with $f/M_{\rm P} <1$. Thus the left panel
  of Fig. (\ref{fig4}) exhibits $f/M_{\rm P}$ as a function of $n_s$ in the range allowed by the Planck data constraint of Eq.(\ref{data})
  and the right panel of Fig. (\ref{fig4}) gives $f/M_{\rm P}$ as a function of $r$
  containing the range in $r$ consistent with the Planck data constraint of Eq.(\ref{data}).

  Finally, we demonstrate in Fig.(\ref{fig5}) that both the Hubble parameter at horizon exit, and
  mass of the inflaton $a_-$ are much smaller than $M_\text{P}$, which are necessary and sufficient
  conditions for the slow-roll approximation to hold.
